Self Regulation Ontology Retest Analyses

### 2018-08-10 code/SRO_Retest_Analyses.Rmd
updated boot task levels plots to only include meaningful vars

```{r}
lit_review %>%
  select(dv, sample_size, task) %>%
  ggplot(aes(sample_size, fill=task))+
  geom_histogram(position = "identity", alpha = 0.5)

rm(p1_t, p2_t, p3_t, mylegend, p1_t_legend)
```

@@

```{r}
trial_num_info = tmp %>%
  group_by(task_group, task) %>%
  summarise(mean_num_all_trials = round(mean(num_all_trials)),
            num_measures = length(unique(dv)))

@@

Boot plot for tasks with trial info

```{r warning=FALSE, message=FALSE}
p4_t <- tmp %>%
  filter(task == 'task') %>%
ggplot(aes(x = factor(task_group, levels=rev(unique(task_group))), y = icc)) + 
  geom_violin(fill='#00BFC4')+
  theme_bw() + 
  theme(axis.text = element_text(size=30))+
  xlab("")+
  ylab("")+
  scale_y_continuous(limits = c(-0.25,1), breaks=c(-0.25, 0, 0.25, 0.5, 0.75, 1), position = "right")+
  scale_x_discrete(labels = function(x) str_wrap(x, width = 15))+
  geom_hline(yintercept = 0, color = "red", size = 1)+
  coord_flip()

@@

Boot plot for surveys with trial info

```{r}
p5_t <- tmp %>%
  filter(task == 'survey') %>%
ggplot(aes(x = factor(task_group, levels=rev(unique(task_group))), y = icc)) + 
  geom_violin(fill='#F8766D')+
  theme_bw() + 
  theme(axis.text = element_text(size=30))+
  xlab("")+
  ylab("")+
  scale_y_continuous(limits = c(-0.25,1), breaks=c(-0.25, 0, 0.25, 0.5, 0.75, 1), position = "right")+
  scale_x_discrete(labels = function(x) str_wrap(x, width = 10))+
  geom_hline(yintercept = 0, color = "red", size = 1)+
  coord_flip()

>>>>

```{r}
rm(p1_t, p2_t, p3_t, mylegend, p1_t_legend)
```

@@

```{r}
tmp_mngfl = tmp %>%
  filter(dv %in% meaningful_vars)

trial_num_info = tmp_mngfl %>%
  group_by(task_group, task) %>%
  summarise(mean_num_all_trials = round(mean(num_all_trials)),
            num_measures = length(unique(dv)))

@@

Boot plot for tasks with trial info (only using meaningful vars)

```{r warning=FALSE, message=FALSE}
p4_t <- tmp_mngfl %>%
  filter(task == 'task') %>%
ggplot(aes(x = factor(task_group, levels=rev(unique(task_group))), y = icc)) + 
  geom_violin(fill='#00BFC4')+
  theme_bw() + 
  theme(axis.text = element_text(size=30))+
  xlab("")+
  ylab("")+
  scale_y_continuous(limits = c(-0.25,1), breaks=c(-0.25, 0, 0.25, 0.5, 0.75, 1), position = "right")+
  scale_x_discrete(labels = function(x) str_wrap(x, width = 15))+
  geom_hline(yintercept = 0, color = "red", size = 1)+
  coord_flip()

@@

Boot plot for surveys with trial info (only using meaningful vars)

```{r}
p5_t <- tmp_mngfl %>%
  filter(task == 'survey') %>%
ggplot(aes(x = factor(task_group, levels=rev(unique(task_group))), y = icc)) + 
  geom_violin(fill='#F8766D')+
  theme_bw() + 
  theme(axis.text = element_text(size=30))+
  xlab("")+
  ylab("")+
  scale_y_continuous(limits = c(-0.25,1), breaks=c(-0.25, 0, 0.25, 0.5, 0.75, 1), position = "right")+
  scale_x_discrete(labels = function(x) str_wrap(x, width = 10))+
  geom_hline(yintercept = 0, color = "red", size = 1)+
  coord_flip()
